The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-12-20 Paper.Rmd
further edits, some tasks for Shyamolina

\begin{figure}[!h]
\begin{center}
\includegraphics[width=3.5in]{./Results/PedagogFig1.pdf}
\caption{(A-F, I, J) Bivariate datasets showing diverse relationships between 
variables; many of these datasets nevertheless have the same Pearson (P)
or Spearman (S) correlation coefficients. Panels C and E (respectively, D and F) were 
obtained from A (respectively, B) via monotonic functions that transformed the standard-
normal marginal distributions of A and B to gamma (C, D) or 
uniform (E, F) marginals (details in Appendix \ref{SM-pedagog1_details}). (G, H) Contours 
of log-scale density functions of Clayton (G) and survival-Clayton 
(H) copulas with parameter 5 (Appendix \ref{SM-pedagog1_details}). (I,J) Reflections
of E, F, respectively, about a vertical axis. Subscripts h and v 
stand for "horizontal" and "vertical". \label{fig_cop_pedag1}}
\end{center}
\end{figure}
<!--***DAN: Dan to go back and add the appendices with details as it says. Make sure
to mention the shape and scale params of the gamma marginals in C, D were 2-->

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm,height=8 cm]{./Results/copula_pedagog_fig_BB1.pdf}
\caption{(A-C) Data generated using the BB1 copula (Methods) with three different 
sets of parameters chosen to produce a variety of 
lower-tail (LT) and upper-tail (UT) dependence strengths (Methods), but the same 
Kendall correlation (KC) (to two digits) in all cases. (D-F) Similar to A-C, but
with stronger correlation. Asymmetry of tail dependence (LT-UT) is the same 
within each column of panels.\label{fig_cop_pedag}}
\end{center}
\end{figure}
<!--***DAN: Shya, I like the grey color of your points on the above figure, 
but I prefer the 
solid plotting symbols and the size of plotting symbols used on the new 
pedagogical figure that I made. Can you please change the code of both figures
so we get grey, with the plotting symbols I used, on both plots? Likeiwse for the 
new figure produced in ./ThirdPedagogFig.R, please. It will be
good to use the same points, for consistency. Don't worry at this stage about
making other figures, other than these three, consistent.-->

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=3.5in]{./Results/PedagogFig3.pdf}
\caption{Log-transformed pdfs (A, C) and samples from (B, D) example copulas.
Shown are the normal copula with parameter $0.8$ and the Frank copula with 
parameter $10$. See also Fig. \ref{fig_cop_pedag1}E-H for the Clayton and  
survival-Clayton copulas with parameter 5, and Appendix \ref{SM-copula_details}
for additional details. \label{fig_cop_pedag3}}
\end{center}
\end{figure}

@@

<!--***DAN: made it to here 2018 12 18 9pm-->

# Results for Q1: Ecological datasets often have non-normal copula structure and asymmetric tail dependence \label{Results}
<!--## question 1
- Do datasets in ecology and related fields have non-Normal copula structure?
- Do they show tail dependence distinct from that of a Normal copula?
- In particular do they show asymmetric tail dependence?

To answer \hyperref[Intro]{\textbf{(Q1)}}, we chose one representative datasets for each category : with a bivariate (soil C and N data) and a multivariate (green spruce aphid-abundance data) dataset, we summarized our findings as follows.
-->

## Results for bivariate data \label{Result_biv}

We summarized our results columnwise in Table \ref{tab_bivar_summary} for different kinds of bivariate datasets (biogeochemical, evolutionary and ecological data) that were plotted in Fig. \ref{fig_biv_multi_raw_cop}(A-H). For all $4$ bivariate-datasets indicated by each column name (SoilCN, Birds' BMR, Mammals' BMR, Ceder-creek) in Table \ref{tab_bivar_summary}, data were always significantly correlated as indicated by p-value (<0.05) from `BiCopIndTest`{`VineCopula`} (1$^{st}$ row of Table \ref{tab_bivar_summary}). Non-Normal copulae always emerged as best fit copula based on minimum AIC value (2$^{nd}$ row of Table \ref{tab_bivar_summary}). The Normal copula was found as poor fit compared to highest AIC-weight based asymmetric copulae (3$^{rd}$ and 4$^{th}$ rows of Table \ref{tab_bivar_summary}) - which answers the first part of \hyperref[Intro]{\textbf{(Q1)}}. Goodness of fit of the best-fit asymmetric copulae were tested based on p-values from two statistics (Cramer-von Mises and Kolmogorov-Smirnov : 5$^{th}$ and 6$^{th}$ rows of Table \ref{tab_bivar_summary}, respectively).
Among 4 datasets presented there, first three have significantly stronger upper tail dependence whereas the last one has significantly stronger lower tail dependence compared to Normal (compare 7$^{th}$ and 8$^{th}$ rows of Table \ref{tab_bivar_summary}). It was indicated by negative AIC-weights model averaged (lower-upper) tail dependence (9$^{th}$ row of Table \ref{tab_bivar_summary}) for first 3 datasets and positive AIC-weights model averaged 
(lower-upper) tail dependence for the last one, which answers the second and third part of \hyperref[Intro]{\textbf{(Q1)}} (For detailed results of each dataset see Tables \ref{SM-tab_soilCNfit} - \ref{SM-tab_cc_asym_2000} and Figs. \ref{SM-fig_soilCN_nonparam} - \ref{SM-fig_cc2000_nonparam}). We also reported the rank of ($\Ps_l - \Ps_u$) for the actual copula data in camparison to the same non-parametric statistics of Kendall-correlation preserving 1000 Normal surrogates. Ranks if were $>$ 975 or $<$ 25, then indicated a significantly (95$\%$ CI) different lower tail-dependence or upper tail-dependence measures, respectively, based on Normal-null hypothesis. We found our model-selection results were consistent with non-parametric analysis for all the datasets (compare last two rows of Table \ref{tab_bivar_summary}).

### Example for bivariate case : soil C and N data shows upper tail dependence\label{Ex_SoilCN}

@@

We will now discuss briefly findings from one of our bivariate datasets as follows. As described in the \nameref{Data}, raw data plot for RaCA database soil organic C and soil N stocks to 1m of soil depth from the central pedon of the `r nrow(d)` sites and their corresponding copula plot were presented in Fig. \ref{fig_biv_multi_raw_cop}(A) and (E), respectively.
We carried out model selection analysis and non-parametric statistics to measure tail-dependence (if any) on this copula plot.

@@

<!--#### Non-parametric analysis of tail dependence \label{Ex_SoilCN_NPA}-->

## Results for multivariate spatial data \label{Result_multi}
```{r read_RES_aphid_count, echo=F}
RES_aphid_count<-readRDS("./Results/fitting_results/AphidCopulaFit_selecloc_count_species_10.RDS")
```

We did model selection and non-parametric analysis with all 20 aphid and 22 plankton species and found our two approaches were consistent to each other. Here, to present our results we chose one species from each category. We summarized our results columnwise in Table \ref{tab_multivar_summary} for all multivariable datasets (i.e., abundance data for green spruce aphid and firstflight date data for leaf-curling plum aphid from `r nrow(RES_aphid_count$gfc_numBS)` sampling locations, abundance data for plankton from UK seas from $14$ sampling locations, 
methane flux data from $13$ sampling locations).

### Example for multivariate case : abundance data for the green spruce aphid (*Elatobium abietinum*) shows spatial synchrony with lower tail dependence\label{Ex_count}

<!--#### Model selection approach \label{Ex_count_Model_selection}-->

As described in \nameref{Model_selection}, for multivariable dataset like green-spruce aphid's abundance data, model selection among copulae was done separately for each pair of the 10 sampling locations, thus results are presented in $10 \times 10$ matrix format with rows and columns corresponding to locations. Table \ref{SM-tab_count_bestcop} shows that, for the large majority of location pairs, some non-Normal copula was a better fit, according to maximum AIC-weights, than was the Normal copula, answering the first part of question \hyperref[Intro]{\textbf{(Q1)}} for these data. Comparing the 
AIC weight of the best-fitting (lowest AIC) copula family for each pair of sampling locations (Table \ref{SM-tab_count_AICw}) to the AIC weight of the Normal copula family for the same pair (Table \ref{SM-tab_count_AICw_normal}) confirms that the degree of support for Normal copulae was usually not
comparable to the degree of support for other families.
Goodness of fit tests based on a Cramer-von Mises statistic (Table \ref{SM-tab_count_p_CvM}) in every case 
failed to reject the hypothesis that the AIC-best copula family was also an objectively adequate description of 
the data, and likewise for goodness of fit tests based on a Kolmogorov-Smirnov statistic (Table \ref{SM-tab_count_p_KS}), demonstrating that the collection of copula families we used was sufficiently broad that the copulae of all pairs of locations could be characterized by at least one of them. In all cases at least `r min((RES_aphid_count$gfc_numBS_success/RES_aphid_count$gfc_numBS),na.rm=T)*100`$\%$ of bootstrap randomizations used for goodness of fit tests successfully lead to values of the statistic for comparison with its value on the real data.

@@

@@

<!--bivariate table summary in latex format-->
```{r tab_bivar_summaryl, echo=F, results='asis',message=F}
tab_bivar_summary<-readRDS("./Results/tab_bivar_summary.RDS")
row.names(tab_bivar_summary)<-NULL
library(kableExtra)
library(dplyr)
library(tibble)
dt <- tibble(Description = c("1. p-value from independence test",
           "2. Best fit copula based on minimum AIC",
           "3. AIC-weight of that best fit copula",
           "4. AIC-weight of Normal copula",
           "5. p-value from goodness of fit test for Cramer-von Mises method",
           "6. p-value from goodness of fit test for Kolmogorov-Smirnov method",
           "7. Model averaged (AIC-weights based) lower tail dependence",
           "8. Model averaged (AIC-weights based) upper tail dependence",
           "9. Model averaged (AIC-weights based) (lower - upper) tail dependence",
           "10. Rank of statistics (Pl-Pu) for real data in comparison to 1000 Normal surrogates")
)
tab_bivar_summary<-cbind(dt,tab_bivar_summary)
knitr::kable(tab_bivar_summary, 
             format="latex", 
             caption = "Summary of results for bivariate data-sets\\label{tab_bivar_summary}",
             booktabs=T, linesep = "\\addlinespace",
             col.names = c(" ", "SoilCN", "Birds’ BMR", "Mammals’ BMR", "Ceder-creek")
             )%>%column_spec(2:5,width="1.4cm")%>%
             column_spec(1, width = "11cm")%>%kable_styling(latex_options = "basic",position = "center")
```

<!--multivariate table summary in latex format-->

```{r tab_multivar_summaryl, echo=F, results='asis',message=F}
tab_multivar_summary<-readRDS("./Results/tab_multivar_summary.RDS")
tab1<-tab_multivar_summary[c(1:7,9,11,12,14,16),] # see carefully if you rearrange tab_multivar_summary's row
                                                   #in suppmat this will change
tab2<-tab_multivar_summary[c(8,10,13,15,17),]  # see carefully if you rearrange tab_multivar_summary's row
                                                   #in suppmat this will change

@@

\begin{figure}[!h]
\textbf{ \hspace{2.8 cm} (A) \hspace{3.2 cm} (B) \hspace{3.2 cm} (C) \hspace{3.2 cm} (D) } \\
\vspace{-0.6 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/SoilCNraw.pdf}
\includegraphics[width=4 cm]{./Results/BMR_results/birds/raw_birds_BMR.pdf}
\includegraphics[width=4 cm]{./Results/BMR_results/mammals/raw_mammals_BMR.pdf}
\includegraphics[width=4 cm]{./Results/Ceder_creek_results/raw_HB_2000.pdf}\\
\end{center}
\textbf{ \hspace{2.8 cm} (E) \hspace{3.2 cm} (F) \hspace{3.2 cm} (G) \hspace{3.2 cm} (H) } \\
\vspace{-0.6 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/SoilCNcop.pdf}
\includegraphics[width=4 cm]{./Results/BMR_results/birds/copula_birds_BMR.pdf}
\includegraphics[width=4 cm]{./Results/BMR_results/mammals/copula_mammals_BMR.pdf}
\includegraphics[width=4 cm]{./Results/Ceder_creek_results/cop_HB_2000.pdf}\\
\end{center}
\textbf{ \hspace{7 cm} (I) \hspace{3.2 cm} (J)} \\
\vspace{-0.6 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/Aphid_count_raw_loc_4_11.pdf}
\includegraphics[width=4 cm]{./Results/Aphid_ff_raw_loc_2_5.pdf}\\
\end{center}
\textbf{ \hspace{7 cm} (K) \hspace{3.2 cm} (L)} \\
\vspace{-0.6 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/Aphid_count_cop_loc_4_11.pdf}
\includegraphics[width=4 cm]{./Results/Aphid_ff_cop_loc_2_5.pdf}
\caption{Upper panel shows raw data plots for \textbf{(A)} soil C and N data, \textbf{(B)} log(BMR) vs. log(mass) for birds, \textbf{(C)} log(BMR) vs. log(mass) for mammals, \textbf{(D)} above-ground plant biomass data vs. Shannon's index (H) averaged over 9m by 9m plots for year 2000 of Ceder-creek experiment.
Middle panel \textbf{(E - H)} shows copula plots for the corresponding datasets of the upper panel. Lower panel shows \textbf{(I - J)} raw data plots and \textbf{(K - L)} copula plots for  green spruce aphid's count data from location pair(4,11) and for leaf-curling plum aphid's firstflight data from location pair(2,5).\label{fig_biv_multi_raw_cop}}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{./Results/PedagogFig1.pdf}
\caption{(A-F, I, J) Bivariate datasets showing diverse relationships between 
variables; many of these datasets nevertheless have the same Pearson (P)
or Spearman (S) correlation coefficients. Panels C and E (respectively, D and F) were 
obtained from A (respectively, B) via monotonic functions that transformed the standard-
normal marginal distributions of A and B to gamma (C, D) or 
uniform (E, F) marginals (details in Appendix \ref{SM-pedagog1_details}). (G, H) Contours 
of log-scale density functions of Clayton (G) and survival-Clayton 
(H) copulas with parameter 5 (Appendix \ref{SM-pedagog1_details}). (I,J) Reflections
of E, F, respectively, about a vertical axis. Subscripts h and v 
stand for "horizontal" and "vertical". \label{fig_cop_pedag1}}
\end{center}
\end{figure}
<!--***DAN: Dan to go back and add the appendices with details as it says. Make sure
to mention the shape and scale params of the gamma marginals in C, D were 2-->

@@

\begin{figure}
\begin{center}
\includegraphics[width=16 cm,height=8 cm]{./Results/copula_pedagog_fig_BB1.pdf}
\caption{(A-C) Data generated using the BB1 copula (Methods) with three different 
sets of parameters chosen to produce a variety of 
lower-tail (LT) and upper-tail (UT) dependence strengths (Methods), but the same 
Kendall correlation (KC) (to two digits) in all cases. (D-F) Similar to A-C, but
with stronger correlation. Asymmetry of tail dependence (LT-UT) is the same 
within each column of panels.\label{fig_cop_pedag}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{./Results/PedagogFig3.pdf}
\caption{Log-transformed pdfs (A, C) and samples from (B, D) example copulas.
Shown are the normal copula with parameter $0.8$ and the Frank copula with 
parameter $10$. See also Fig. \ref{fig_cop_pedag1}E-H for the Clayton and  
survival-Clayton copulas with parameter 5, and Appendix \ref{SM-copula_details}
for additional details. \label{fig_cop_pedag3}}
\end{center}
\end{figure}

@@

# Results for Q1: Ecological datasets often have non-normal copula structure and asymmetric tail dependence \label{Results}

@@

```{r read_RES_aphid_count, echo=F}
RES_aphid_count<-readRDS("./Results/fitting_results/AphidCopulaFit_selecloc_count_species_10.RDS")
```

Across essentially all the sub-fields and levels of organization within ecology that we 
examined, copula structures were typically non-normal and variables exhibited asymmetric tail 
dependence. To make results easier for readers who are new to copulas to absorb: we first 
present results in detail for an example bivariate dataset; followed by a summary of results
for all bivariate datasets; then we present results in 
detail for an example multivariate dataset; followed by a summary of results 
for all multivariate datasets.

<!--bivariate example-->
We will now discuss briefly findings from one of our bivariate datasets as follows. As described in the \nameref{Data}, raw data plot for RaCA database soil organic C and soil N stocks to 1m of soil depth from the central pedon of the `r nrow(d)` sites and their corresponding copula plot were presented in Fig. \ref{fig_biv_multi_raw_cop}(A) and (E), respectively.
We carried out model selection analysis and non-parametric statistics to measure tail-dependence (if any) on this copula plot.

@@

<!--bivariate summary-->
We summarized our results columnwise in Table \ref{tab_bivar_summary} for different kinds of bivariate datasets (biogeochemical, evolutionary and ecological data) that were plotted in Fig. \ref{fig_biv_multi_raw_cop}(A-H). For all $4$ bivariate-datasets indicated by each column name (SoilCN, Birds' BMR, Mammals' BMR, Ceder-creek) in Table \ref{tab_bivar_summary}, data were always significantly correlated as indicated by p-value (<0.05) from `BiCopIndTest`{`VineCopula`} (1$^{st}$ row of Table \ref{tab_bivar_summary}). Non-Normal copulae always emerged as best fit copula based on minimum AIC value (2$^{nd}$ row of Table \ref{tab_bivar_summary}). The Normal copula was found as poor fit compared to highest AIC-weight based asymmetric copulae (3$^{rd}$ and 4$^{th}$ rows of Table \ref{tab_bivar_summary}) - which answers the first part of \hyperref[Intro]{\textbf{(Q1)}}. Goodness of fit of the best-fit asymmetric copulae were tested based on p-values from two statistics (Cramer-von Mises and Kolmogorov-Smirnov : 5$^{th}$ and 6$^{th}$ rows of Table \ref{tab_bivar_summary}, respectively).
Among 4 datasets presented there, first three have significantly stronger upper tail dependence whereas the last one has significantly stronger lower tail dependence compared to Normal (compare 7$^{th}$ and 8$^{th}$ rows of Table \ref{tab_bivar_summary}). It was indicated by negative AIC-weights model averaged (lower-upper) tail dependence (9$^{th}$ row of Table \ref{tab_bivar_summary}) for first 3 datasets and positive AIC-weights model averaged 
(lower-upper) tail dependence for the last one, which answers the second and third part of \hyperref[Intro]{\textbf{(Q1)}} (For detailed results of each dataset see Tables \ref{SM-tab_soilCNfit} - \ref{SM-tab_cc_asym_2000} and Figs. \ref{SM-fig_soilCN_nonparam} - \ref{SM-fig_cc2000_nonparam}). We also reported the rank of ($\Ps_l - \Ps_u$) for the actual copula data in camparison to the same non-parametric statistics of Kendall-correlation preserving 1000 Normal surrogates. Ranks if were $>$ 975 or $<$ 25, then indicated a significantly (95$\%$ CI) different lower tail-dependence or upper tail-dependence measures, respectively, based on Normal-null hypothesis. We found our model-selection results were consistent with non-parametric analysis for all the datasets (compare last two rows of Table \ref{tab_bivar_summary}).

<!--multivariate example-->
As described in \nameref{Model_selection}, for multivariable dataset like green-spruce aphid's abundance data, model selection among copulae was done separately for each pair of the 10 sampling locations, thus results are presented in $10 \times 10$ matrix format with rows and columns corresponding to locations. Table \ref{SM-tab_count_bestcop} shows that, for the large majority of location pairs, some non-Normal copula was a better fit, according to maximum AIC-weights, than was the Normal copula, answering the first part of question \hyperref[Intro]{\textbf{(Q1)}} for these data. Comparing the 
AIC weight of the best-fitting (lowest AIC) copula family for each pair of sampling locations (Table \ref{SM-tab_count_AICw}) to the AIC weight of the Normal copula family for the same pair (Table \ref{SM-tab_count_AICw_normal}) confirms that the degree of support for Normal copulae was usually not
comparable to the degree of support for other families.
Goodness of fit tests based on a Cramer-von Mises statistic (Table \ref{SM-tab_count_p_CvM}) in every case 
failed to reject the hypothesis that the AIC-best copula family was also an objectively adequate description of 
the data, and likewise for goodness of fit tests based on a Kolmogorov-Smirnov statistic (Table \ref{SM-tab_count_p_KS}), demonstrating that the collection of copula families we used was sufficiently broad that the copulae of all pairs of locations could be characterized by at least one of them. In all cases at least `r min((RES_aphid_count$gfc_numBS_success/RES_aphid_count$gfc_numBS),na.rm=T)*100`$\%$ of bootstrap randomizations used for goodness of fit tests successfully lead to values of the statistic for comparison with its value on the real data.

@@

<!--multivariate summary-->
We did model selection and non-parametric analysis with all 20 aphid and 22 plankton species and found our two approaches were consistent to each other. Here, to present our results we chose one species from each category. We summarized our results columnwise in Table \ref{tab_multivar_summary} for all multivariable datasets (i.e., abundance data for green spruce aphid and firstflight date data for leaf-curling plum aphid from `r nrow(RES_aphid_count$gfc_numBS)` sampling locations, abundance data for plankton from UK seas from $14$ sampling locations, 
methane flux data from $13$ sampling locations).

@@

<!--bivariate table summary in latex format-->
```{r tab_bivar_summaryl, echo=F, results='asis',message=F}
tab_bivar_summary<-readRDS("./Results/tab_bivar_summary.RDS")
row.names(tab_bivar_summary)<-NULL
library(kableExtra)
library(dplyr)
library(tibble)

dt <- tibble(Description = c("1. P-value, independence test",
           "2. Minimum-AIC copula",
           "3. AIC weight of minimum-AIC copula",
           "4. AIC weight of N copula",
           "5. P-value, Cramer-von Mises goodness of fit test",
           "6. P-value, Kolmogorov-Smirnov goodness of fit test",
           "7. Model averaged lower-tail dependence",
           "8. Model averaged upper-tail dependence",
           "9. Model averaged lower- minus upper-tail dependence",
           "10. Asymmetry rank in surrogates")
)
tab_bivar_summary<-cbind(dt,tab_bivar_summary)
knitr::kable(tab_bivar_summary, 
             format="latex",
             caption = "Summary of Q1 results for bivariate datasets. The $p$-values in rows 5-6 and are for the minimum-AIC copula. Model averaging used for rows 7-9 was based on AIC weights. For row 10, the statistic $P_l-P_u$ was computed for real data and for 1000 surrogate datasets with N copulas, and the rank of real-data value in the distribution of surrogate values is presented. \\label{tab_bivar_summary}",
             booktabs=T, linesep = "\\addlinespace",
             col.names = c(" ", "Soil C and N", "Bird masses and BMR", "Mammal masses and BMR", "Cedar creek data")
             )%>%column_spec(2:5,width="1.4cm")%>%
             column_spec(1, width = "8.5cm")%>%kable_styling(latex_options = "basic",position = "center")
```
<!--***DAN: Shya, it says Pl-Pu above, but I suspect it was P_first slice - P_last slice, right?
Can you please look back at the code, if necessary, and write a comment below this one 
indicating what results are actually presented in the table?-->

<!--multivariate table summary in latex format-->
```{r tab_multivar_summaryl, echo=F, results='asis',message=F}
tab_multivar_summary<-readRDS("./Results/tab_multivar_summary.RDS")
tab1<-tab_multivar_summary[c(1:7,9,11,12,14,16),] # see carefully if you rearrange tab_multivar_summary's row
                                                   #in suppmat this will change
tab2<-tab_multivar_summary[c(8,10,13,15,17),]  # see carefully if you rearrange tab_multivar_summary's row
                                                   #in suppmat this will change

@@

\begin{figure}
\begin{center}
\includegraphics[width=6.5in]{./Results/BivarDataPlot.pdf}
\caption{Upper panels shows raw data plots for (A) soil C and N data, (B) $log_{10}$(basal metabolic rate (BMR)) vs. log(body mass) 
for birds, (C) log(BMR) vs. log(body mass) for mammals, and (D) above-ground plant biomass vs. Shannon's index (H) from Cedar Creek. Bottom panels show the corresponding copula plots. \label{fig_biv_multi_raw_cop}}
\end{center}
\end{figure}
<!--***DAN: Shya, we need to produce a single-pdf figure using R, not use latex to
cobble together separate pdfs for each panel. Also, I think we can dispense with the 
plots of the multivariate data. I have created a script that will do both of these things, 
and inserted a call to it in the sup mat Rmd. Right now it only plots dummy, filler data. 
Please look at MakeBivarDataPlot.R (that's the script) and search for
"Shya", and do as it says in those comments, so the actual data are imported into that
script and plotted. I have changed the above so this new figure is plotted instead of the
cobbled together old figures.-->
